---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# manifoldr

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![Codecov test coverage](https://codecov.io/gh/jcblsn/manifoldr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jcblsn/manifoldr?branch=main)

<!-- badges: end -->

The goal of `manifoldr` is to streamline interactions between R users and the [Manifold Markets](https://manifold.markets/home) API. The Manifold Markets API documentation can be found [here](https://docs.manifold.markets/api). All endpoints are supported as of November 2022.

<!-- apis in r https://cran.r-project.org/web/packages/httr/vignettes/api-packages.html -->

<!-- secret management https://httr2.r-lib.org/articles/wrapping-apis.html#secret-management -->

<!-- codecov https://github.com/marketplace/actions/codecov -->

<!-- can update locally by running covr::codecov() with token, o/w it'll update when i push to github --> <!-- testing https://r-pkgs.org/testing-basics.html --> 

<!-- create new test with usethis::use_test("get_manifold_api_key.R") --> 

<!-- add package to DESCRIPTION (still need to specify @import where relevant for it to be included in NAMESPACE) after roxygen2::roxygenize() devtools::use_package('tibble') --> 

<!-- run all tests locally testthat::test_local() -->

## Installation

You can install the development version of `manifoldr` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jcblsn/manifoldr")
```

## Examples

Users can reference the core function `manifold_api()` with any endpoint using the instructions given in the documentation.

```{r, eval = F}
manifoldr::manifold_api(
  endpoint = "/v0/user/ManifoldMarkets", 
  request_type = "GET"
)
```

A number of convenience functions are also provided. These include functions for specific endpoints and others such as `clean_manifold_content()`, which returns output as a data frame with clean variable names.

```{r, eval = F}
manifoldr::get_markets(n_markets = 3) |> 
  manifoldr::clean_manifold_content()
```

## Code of Conduct

Please note that the `manifoldr` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
